%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.5in,top=0.6in,right=0.6in,bottom=0.6in]{geometry} % Document margins
\usepackage{tabularx}

\name{Matt Lim} % Your name

\address{mlim@caltech.edu \\ (925)~$\cdot$~639~$\cdot$~4576
    \\ 1200 E. California Blvd, Pasadena CA, 91126} % Your address

%\address{122 Ardith Drive \\ Orinda, CA 94563} % Your secondary addess (optional)
%\address{(925)~$\cdot$~639~$\cdot$~4576 \\ mlim@caltech.edu} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf California Institute of Technology} \hfill {\em 2013 - 2017} \\
B.S. in Computer Science \smallskip \\
Overall GPA: 4.0 \\
TA for EE150: Digital Ventures Design \\
Caltech Basketball team 13-14 \smallskip \\
Relevant Coursework:
\vspace{-5.0mm}
\begin{minipage}{0.4\linewidth}
\begin{itemize}
\item{CS38: Intro to Algorithms}
\item{CS122: Database System Implementation}
\end{itemize}
\end{minipage}
\begin{minipage}{0.4\linewidth}
\begin{itemize}
    \item{CS24: Intro to Computing Systems}
\item{CS156b: Machine Learning Systems}
\end{itemize}
\end{minipage}
\vspace{2mm}
\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills \& Abilities}

\begin{tabularx}{\textwidth}{@{}lX}
    \bfseries{Computer Languages}   &  Java, C, C++, Python, SQL, Scheme, Objective-C, Swift,  \\
    \bfseries{Technologies \& Platforms}   &  Apache Spark, ANTLR, AWS, Android, iOS, libGDX \\
    \bfseries{Operating Sysems}   &  Linux, OS X \\
    \bfseries{Tools}   &  Vim, Git, SVN, Terminal, Inkscape, \LaTeX \\
\end{tabularx}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience \& Projects}

    \begin{rSubsection}{Intern at Salesforce}{Summer 2015}{Developer}{San Francisco, CA}
\item Worked on backend of platform for batch big data processing.
\item Performance tested JSON/Avro serialization in Spark pipeline.
\item Worked on designing new language to act as intermediary between UI and HiveQL.
\item Analyzed high level Salesforce use case and converted the corresponding SQL stored procedures to
    our new language.
\item Wrote ANTLR grammar for new language, along with logic to convert it into the corresponding HiveQL.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Intern at Aspera}{Summer 2014}{iOS Developer}{Emeryville, CA}
\item Brought company's main app, Faspex, to an iOS 7 release. Large refactors in
    UI and video encoding.
\item Developed two sample apps in Swift to demonstrate proper use of Aspera's iPhone
    SDK.
\item Created a Share Extension for Faspex data transfers and a Document/File Provider Extension
    for Faspex file sharing.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Stairs - stairsthegame.com }{January 2014 - August 2014}{Developer}{California}
\item Developed an original "infinite stepper" game with 8 game modes,
    5 level types, and custom music and icons.
\item Created using the Java libGDX framework. Available for iOS, Android, and Desktop.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{OmNotify}{Summer 2013}{Founder \& Developer}{California}
\item Developed an Android app that makes, augments, edits, and stores notifications.
\item Notifications allow custom vibrations, alarms, reminders, and schedules.
\item Notifications can be sent to SMS contacts.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{GoogleJump Mentorship Program}{Summer 2014}{Participant}{California}
\item Worked with 2 other participants and a Google engineer mentor to create Aux,
    an Android app that utilizes the Places and Location APIs in order to smartly
    and automatically toggle various phone settings.
\item Used a SQLite database to support custom profiles that dictate how the phone behaves
    under certain actions/locations.
\end{rSubsection}

\end{rSection}



%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Additional Information}

\noindent\begin{tabularx}{.98\textwidth}{@{}lX}
    \bfseries{Additional Projects}   &  Othello AI (6th place out of 60+ Caltech
    students), Caltech Open (Android app that tells students if and when
    buildings and services are open), Simple SMS (Android SMS client) \\
    \bfseries{Miscellaneous}   &  Lifeguard, Red Cross and CPR Certified, Basketball
    Coach \\
\end{tabularx}

\end{rSection}

\end{document}
